SMT-Boosted Security Types and Correctness for Low-Level MPC

### 2025-12-11 toplas26/examples.tex
yet another update

@@

\subsection{Evaluation}
We have implemented the $\metaprot$ language and automated Hoare logic
using an Antlr parser and Scala backend with cvc5 Java bindings for
interaction with proof engines.  To evaluate performance, we have
written and verified gate libraries using the GMW protocol for binary
circuits as excerpted in Figure \ref{fig-gmwprepost} in Section
\ref{section-metalang}, and for passive and malicious secure
arithmetic circuits using Beaver Triple multiplication as presented in
Figures \ref{fig-beaver} and \ref{fig-beaver-bdoz} in this Section.
We have considered field sizes typically used to encode binary, 16
bit, 32 bit, and 64 bit integers. Results are presented in Figure
\ref{fig-preludetest}. We found that verification of library
components was efficient even up to large field sizes. Since typing is
compositional (see, e.g., Figure \ref{fig-beaver-types}), verification
of gate properties relevant to \emph{security} will scale to larger
circuits.

>>>>

\subsection{Evaluation}

We have implemented the $\metaprot$ language and automated Hoare logic
using an Antlr parser and Scala backend with cvc5 Java bindings for
interaction with proof engines.  To evaluate performance, we have
written and verified gate libraries using the GMW protocol for binary
circuits as excerpted in Figure \ref{fig-gmwprepost} in Section
\ref{section-metalang}, and for passive and malicious secure
arithmetic circuits using Beaver Triple multiplication as presented in
Figures \ref{fig-beaver} and \ref{fig-beaver-bdoz} in this Section.
We have considered field sizes typically used to encode binary, 16
bit, 32 bit, and 64 bit integers. Results are presented in Figure
\ref{fig-preludetest}. We found that verification of library
components was efficient even up to large field sizes. Since typing is
compositional (see, e.g., Figure \ref{fig-beaver-types}), verification
of gate properties relevant to \emph{security} will scale to larger
circuits.

@@
